How do language models represent a relational operation ---
\emph{currency-of}, \emph{capital-of} --- as distinct from the entity it
applies to? We separate three levels of evidence.
\textbf{Representation:} a two-way ANOVA factorizes the mid-network
state as \texttt{H\ \ensuremath{\approx}\ \ensuremath{\mu}\ +\ operand\ +\ operator\ +\ interaction},
\textasciitilde90\% additive across Qwen3-1.7B/8B and Gemma-2-9B --- and
the steering vector is \emph{identically} the ANOVA operator component.
\textbf{Causal influence:} adding \texttt{v(op\_B)\ -\ v(op\_A)} flips
the target-vs-source logit margin for all ordered relation pairs in all
three models; the query token alone matches the full-prompt effect at
60\ensuremath{\times} lower off-task cost, and the decisive nulls --- directions rebuilt
under \textbf{permuted relation labels}, and random directions
\textbf{inside the operator subspace} --- abolish the effect.
\textbf{Behavioral sufficiency:} a state \emph{composed} from the
factorization\textquotesingle s parts,
\texttt{\ensuremath{\mu}\ +\ operand\ +\ operator}, patched at one position, makes the
model \emph{produce} the target answer at its own competence ceiling
(52\% vs. 53\% clean; leave-one-out components reach 36\%, and swapping
the operand component redirects the answer). The interaction term is
unnecessary --- and the earlier failure of additive steering to generate
is a \textbf{dose artifact}: at the calibrated dose the same direction
generates at ceiling, while overdosing keeps inflating the margin as it
pushes the state off-manifold. The structure generalizes (held-out
operands, re-framed and re-lexicalized prompts, an independent
animal-taxonomy domain), separates the operation from its surface
realization (\emph{language-of} \ensuremath{\neq} \emph{demonym-of} despite both
emitting "Italian"), and does not emerge for arithmetic or logic under
the identical pipeline. Relational computation here is an operand plus a
transplantable operator --- sufficient, not merely influential, where
the answer is decided.
