\section{Reproducibility, stimuli, and implementation
details}

\textbf{Checkpoints and hardware.} \texttt{Qwen/Qwen3-1.7B},
\texttt{Qwen/Qwen3-8B}, \texttt{google/gemma-2-9b}, all bf16 on a single
AMD Strix Halo APU (128 GB unified memory, ROCm PyTorch). Seeds default
to 0 and affect only the random controls; direction building is
deterministic.

\textbf{Stimuli.} Operands (12 countries): Italy, Japan, Russia, China,
France, Germany, Brazil, Egypt, India, Mexico, Sweden, Turkey.
Relations: currency, capital, language, demonym ("word for a person
from"), continent; every (country, relation) cell has a gold one-word
answer (e.g. Italy \ensuremath{\to} euro, Rome, Italian, Italian, Europe); the full
grid ships in \texttt{data/relations.json}, the lexical reformulations
in \texttt{data/relations\_lex.json}, and the paraphrase frames in the
dataset metadata.

\textbf{Answer scoring and selection.} Answers are scored at the first
token of \texttt{"\ "\ +\ answer}. Within each ordered operator pair,
operands whose two answers collide at that token are dropped (4 of 12
survive on the syncretic demonym\ensuremath{\leftrightarrow}language pairs; all 12 elsewhere).
Whole-word single-token coverage: 0.92 (Qwen3 BPE), 0.95 (Gemma
SentencePiece).

\textbf{Directions, interventions, and controls.}
\texttt{v(op){[}layer{]}} is the mean over (operand, frame) cells of the
op\textquotesingle s residual minus that cell\textquotesingle s mean
over ops, computed at \textasciitilde25 evenly spaced source layers
restricted to the 38--92\% depth band. Interventions add
\texttt{\ensuremath{\alpha}\ \textperiodcentered{}\ (v(to)\ -\ v(from))} at every position of the band (\ensuremath{\alpha} = 4
unless swept). The matched-norm control draws one Gaussian vector per
layer and rescales the band-concatenated stack to exactly the injected
difference\textquotesingle s norm. Clean mean margins
\texttt{logit(to)\ -\ logit(from)} are \ensuremath{\approx} -7 to -8 across models and
frames; per-operand values for every experiment are released as
long-form artifacts (\texttt{results/ablation/*\_long.parquet}).

\textbf{Experiment drivers.} \texttt{op\_core.py} (directions, swaps,
ANOVA, cluster bootstraps), \texttt{operator\_paradigm.py},
\texttt{operator\_factorize.py}, \texttt{operator\_templates.py},
\texttt{operator\_lexical.py}, \texttt{op\_dose.py},
\texttt{op\_minimal.py}, \texttt{op\_geometry\_dump.py}.

\section{The J-space readout
comparisons}

Four readout comparisons on Qwen3-1.7B (8B where noted) asked whether
the Jacobian-lens readout exposes more than the logit lens:
bridge-entity pass@k (a tie, drifting toward the logit lens at 8B); a
surface-form logit difference with real competitors (logit lens matches
or wins in every depth band); a grammatical-number probe with
Hewitt--Liang selectivity (number decodable at ceiling from \emph{all}
lenses --- including a \textbf{spectrum-matched random projection}, the
decisive control); and the concept-plane trajectory that motivated the
project (the J-lens path is longer on random planes too --- a generic
magnitude effect, not a concept channel). A permuted-vocabulary lens
control behaves accordingly. The 1.7B readout-geometry difference (cases
reorganizing by output form in J-space) does not replicate at 8B and is
not relied on. Full tables live in the project\textquotesingle s working
log.


